### 2016-04-08 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Added some HRR data for gas burner experiments

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests---Test~2, Test~3, Test~4, Test~5, and Test~6---were conducted in the East Structure. Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for Tests~2--4. The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved performing a specific set of events three times sequentially. To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table).

@@

>>>>

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests---Test~2, Test~3, Test~4, Test~5, and Test~6---were conducted in the East Structure. Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for Tests~2--4. The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved performing a specific set of events three times sequentially. To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table). Additionally, Table~\ref{table:HRR_East} lists the calculated heat release rate for each test and sequence.

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
% \begin{tabular}{lccccc}
%  \toprule
%  					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
% \textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
% 					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
% 					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
% 					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
% 					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
%  \midrule
% Test 2 				& 360 & 690	& 950 & 680 & 350 \\
% Test 3				& 360 & 690	& 950 & 680 & 350 \\
% Test 4				& 360 & 690	& 950 & 680 & 350 \\
% Test 5 - Seq. 1		& 360 & 690	& 950 & 680 & 350 \\
% Test 5 - Seq. 2		& 360 & 690	& 950 & 680 & 350 \\
% Test 5 - Seq. 3		& 360 & 690	& 950 & 680 & 350 \\
% Test 6 - Seq. 1		& 360 & 690	& 950 & 680 & 350 \\
% Test 6 - Seq. 2		& 360 & 690	& 950 & 680 & 350 \\
% Test 6 - Seq. 3		& 360 & 690	& 950 & 680 & 350 \\
\begin{tabular}{lc}
 \toprule
\textbf{Test}  		& 	\textbf{Heat Release Rate (kW)} \\
\midrule
Test 2 				& 			\\
Test 3				& 			\\
Test 4				& 	949		\\
Test 5 - Seq. 1		&  	723		\\
Test 5 - Seq. 2		&  	728		\\
Test 5 - Seq. 3		&  	724	    \\
Test 6 - Seq. 1		&  	718	    \\
Test 6 - Seq. 2		&   714     \\
Test 6 - Seq. 3		&   716	 	\\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
\begin{tabular}{lc}
 \toprule
\textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
\midrule
Test 22 				& 	756		\\
Test 23					& 	788		\\
Test 24					& 	784		\\
Test 25					&  	785		\\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}
